Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond

### 2024-02-15 outputs/paper/paper.qmd
Update paper.qmd

---
title: "Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond"
subtitle: "Reproduction of 'The Puzzle of Falling US Birth Rates since the Great Recession'(Kearney, Levine & Pardue, 2022)"
author: 
  - Chay Park
thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Social-Science-Study."
date: today
date-format: long
abstract: "This paper examines the notable decrease in US birth rates from 2007 to 2020, replicating the study conducted by Kearney, Levine, and Pardue (2022). Through an analysis of trends spanning from 1980 to 2020, we investigate variations in birth rates among different age groups and disparities based on the race and ethnicity of mothers. While initially attributing the decline to the Great Recession, our analysis uncovers additional factors contributing to this trend. Furthermore, our exploration delves into socio-cultural aspects, offering insights for policymakers and researchers interested in population trends and their implications."
format: pdf
number-sections: true
bibliography: references.bib
prefer-html: true
---

>>>>

---
title: "Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond"
subtitle: "Reproduction of 'The Puzzle of Falling US Birth Rates since the Great Recession'(Kearney, Levine & Pardue, 2022)"
author: 
  - Chay Park
thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Social-Science-Study. A replication of various aspects in this paper are available at: https://doi.org/10.48152/ssrp-srs6-t802""
date: today
date-format: long
abstract: "This paper examines the notable decrease in US birth rates from 2007 to 2020, replicating the study conducted by Kearney, Levine, and Pardue (2022). Through an analysis of trends spanning from 1980 to 2020, we investigate variations in birth rates among different age groups and disparities based on the race and ethnicity of mothers. While initially attributing the decline to the Great Recession, our analysis uncovers additional factors contributing to this trend. Furthermore, our exploration delves into socio-cultural aspects, offering insights for policymakers and researchers interested in population trends and their implications."
format: pdf
number-sections: true
bibliography: references.bib
prefer-html: true
---
